Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-12-02 index.qmd
Update index.qmd

| Group                              | n   | n_pos | n_neg | perc_pos | perc_neg |
|------------------------------------|-----|-------|-------|----------|----------|
| Precipitation - Monsoon Dominated  | 87  | 8     | 21    | 0.092    | 0.241    |
| Precipitation - Snowmelt Dominated | 118 | 9     | 12    | 0.076    | 0.102    |
| PhysRegion - Basin&Range           | 156 | 14    | 26    | 0.090    | 0.167    |
| PhysRegion - CO Plateau            | 49  | 3     | 7     | 0.061    | 0.143    |
| Climate - Warm-Wet                 | 31  | 2     | 6     | 0.065    | 0.194    |
| Climate - Warm-Dry                 | 55  | 6     | 11    | 0.109    | 0.200    |
| Climate - Cool-Wet                 | 74  | 4     | 9     | 0.054    | 0.122    |
| Climate - Cool-Dry                 | 45  | 5     | 7     | 0.111    | 0.156    |
| Slope - High                       | 102 | 10    | 12    | 0.098    | 0.118    |
| Slope - Low                        | 103 | 7     | 21    | 0.068    | 0.204    |

@@

| Classification Group               | n    | R^2^  | MSE    | RMSE  | MAE   | NSE   | pbias |
|----------------|--------|--------|--------|--------|--------|--------|--------|
| Precipitation - Monsoon Dominated  | 3345 | 0.707 | 0.0166 | 0.129 | 0.077 | 0.694 | -12.6 |
| Precipitation - Snowmelt Dominated | 6152 | 0.723 | 0.017  | 0.131 | 0.094 | 0.715 | -3.7  |
| PhysRegion - Basin&Range           | 7754 | 0.749 | 0.018  | 0.133 | 0.089 | 0.741 | -5.9  |
| PhysRegion - CO Plateau            | 1743 | 0.806 | 0.013  | 0.115 | 0.081 | 0.801 | -4.4  |
| Climate - Warm-Wet                 | 1613 | 0.690 | 0.015  | 0.124 | 0.081 | 0.679 | -9.9  |
| Climate - Warm-Dry                 | 3134 | 0.758 | 0.023  | 0.151 | 0.097 | 0.745 | -8.1  |
| Climate - Cool-Wet                 | 3134 | 0.710 | 0.013  | 0.115 | 0.085 | 0.708 | -2.5  |
| Climate - Cool-Dry                 | 1616 | 0.809 | 0.014  | 0.118 | 0.082 | 0.803 | -5    |
| Slope - High                       | 4398 | 0.753 | 0.014  | 0.120 | 0.084 | 0.746 | -4.4  |
| Slope - Low                        | 5099 | 0.759 | 0.019  | 0.138 | 0.090 | 0.750 | -6.9  |

>>>>

| Classification Group               | n   | n_pos | n_neg | perc_pos | perc_neg |
|------------------------------------|-----|-------|-------|----------|----------|
| Precipitation - Monsoon Dominated  | 87  | 8     | 21    | 0.092    | 0.241    |
| Precipitation - Snowmelt Dominated | 118 | 9     | 12    | 0.076    | 0.102    |
| PhysRegion - Basin&Range           | 156 | 14    | 26    | 0.090    | 0.167    |
| PhysRegion - CO Plateau            | 49  | 3     | 7     | 0.061    | 0.143    |
| Climate - Warm-Wet                 | 31  | 2     | 6     | 0.065    | 0.194    |
| Climate - Warm-Dry                 | 55  | 6     | 11    | 0.109    | 0.200    |
| Climate - Cool-Wet                 | 74  | 4     | 9     | 0.054    | 0.122    |
| Climate - Cool-Dry                 | 45  | 5     | 7     | 0.111    | 0.156    |
| Slope - High                       | 102 | 10    | 12    | 0.098    | 0.118    |
| Slope - Low                        | 103 | 7     | 21    | 0.068    | 0.204    |

@@

| Classification Group           |  n    |   R2  |  MSE  |  RMSE |  MAE  | NSE            | pbias |
|---------------------------------|------|-------|-------|-------|-------|----------------|-------|
| Climate - Monsoon Dominated     | 3039 | 0.633 | 0.016 | 0.126 | 0.074 | 0.619          | -13.7 |
| Climate - Snowmelt Dominated    | 4685 | 0.733 | 0.015 | 0.121 | 0.087 | 0.725          |  -3.5 |
| PhysRegion - Basin&Range        | 6147 | 0.733 | 0.016 | 0.127 | 0.084 | 0.724          |  -6.3 |
| PhysRegion - CO Plateau         | 1577 | 0.846 | 0.011 | 0.104 | 0.073 | 0.843          |  -3.8 |
| Climate - Warm-Wet              | 1506 | 0.693 | 0.014 | 0.117 | 0.077 | 0.685          |  -8.2 |
| Climate - Warm-Dry              | 2351 | 0.693 | 0.022 | 0.147 | 0.092 | 0.675          | -11.9 |
| Climate - Cool-Wet              | 2350 | 0.738 | 0.011 | 0.106 | 0.078 | 0.736          |  -1.7 |
| Climate - Cool-Dry              | 1517 | 0.831 | 0.012 | 0.111 | 0.078 | 0.827          |  -4.3 |
| Slope - High                    | 3795 | 0.776 | 0.012 | 0.111 | 0.079 | 0.771          |  -3.3 |
| Slope - Low                     | 3929 | 0.724 | 0.018 | 0.133 | 0.085 | 0.713          |  -9.1 |
